The WebID Protocol and Access Delegation

### 2012-09-07 paper.tex
shortened title

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}
\def\sectionautorefname{Section}% redefine the label for section links

\title{Extending the WebID Protocol with Access Delegation}

>>>>

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
pdftitle={The WebID Protocol and Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}
\def\sectionautorefname{Section}% redefine the label for section links

\title{The WebID Protocol and Access Delegation}
